Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-21 paper/paper.tex
Change overly clever wording
Typo

For MCCS we consider only undirected graphs (and so we treat directed edges in the inputs as being
undirected). For directed graphs, there is more that one notion of connectivity, and it is not clear
which should be selected---the approaches we consider extend easily to weakly connected directed
graphs, but not to the strongly connected case.

@@

In \cref{figure:connected-cumulative} we compare the clique-based approach to the connected problem
with both CP Both approaches. The trend is broadly similar to the unconnected problem: for labelled
graphs, the clique-based approach is the clear winner, but for unlabelled graphs the clique approach
lags somewhat.

>>>>

For MCCS we consider only undirected graphs (and so we treat directed edges in the inputs as being
undirected). For directed graphs, there is more than one notion of connectivity, and it is not clear
which should be selected---the approaches we consider extend easily to weakly connected directed
graphs, but not to the strongly connected case.

@@

In \cref{figure:connected-cumulative} we compare the clique-based approach to the connected problem
with the two CP Both approaches. The trend is broadly similar to the unconnected problem: for labelled
graphs, the clique-based approach is the clear winner, but for unlabelled graphs the clique approach
lags somewhat.
